OptiFit: a fast method for fitting sequences to existing OTUs for microbial ecology

### 2021-03-11 docs/slides/2021-03-11_bistro.Rmd
Minor updates

---
title: "Comparing microbial communities with OptiFit: a fast method for fitting sequences to existing OTUs"
subtitle: ""
author: "Kelly Sovacool"
date: "2021-03-11"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      #titleSlideClass: ['center', 'middle', 'title-slide']
    chakra: libs/remark-latest.min.js
    self_contained: true
---

@@

@@

>>>>

---
title: "OptiFit: a fast method for fitting sequences to existing OTUs for microbial ecology"
subtitle: ""
author: "Kelly Sovacool"
date: "2021-03-11"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
      #titleSlideClass: ['center', 'middle', 'title-slide']
    chakra: libs/remark-latest.min.js
    self_contained: true
---

@@

???
Human Microbes: The Power within (2018)

[The Human Microbiome Project (2012) Nature](https://dx.doi.org/10.1038%2Fnature11234)

@@

mothur: command line program for processing amplicon sequence data and comparing microbial communities
